---
title: "Hw1"
author: "Yu Si"
date: "9/29/2021"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
library(dplyr)
```

##Problem 1

###1.1
```{r}
set.seed(1234)
#Create the data frame
problem_df = tibble(
  x = rnorm(10),
  vec_logical = c(FALSE, FALSE, TRUE, FALSE,FALSE,TRUE,TRUE,TRUE,FALSE,FALSE),
  vec_char =  character(10),
  vec_factor = factor(c("Level1", "Level2", "Level3","Level1", "Level2", "Level3","Level1", "Level2", "Level3","Level2"))
  )
problem_df
#pull the variable out of data frame
col_1 = pull(problem_df, var=1)
col_2 = pull(problem_df, var=2)
col_3 = pull(problem_df, var=3)
col_4 = pull(problem_df, var=4)
col_1
col_2
col_3
col_4
#calculate the mean of each variable
mean(col_1)
mean(col_2)
mean(col_3)
mean(col_4)

```
Based on the results, the numeric and logical variables work and others don't work for calculating mean.

###1.2

```{r, results = 'hide'}
col_2_numeric = as.numeric(col_2)
col_3_numeric = as.numeric(col_3)
col_4_numeric = as.numeric(col_4)
```
After converting variables from one type to another, I find that the logical variables become 0 and 1 because of the binary characteristic, which explains that the mean of this variable is 0.4 because there are four "1" in 10 numbers. The character what i create is 10 length but it is all empty. Then using as.numeric, the results are 10 NA. When a factor is converted into a numeric vector, the numeric codes corresponding to the factor levels will be returned. 

##Problem 2
```{r}
data("penguins", package = "palmerpenguins")
summary(penguins)
nrow(penguins)
ncol(penguins)
flipper_length_mean = mean(penguins$flipper_length_mm, na.rm=TRUE)
```
There 344 observation of 8 variables. The variables are species, island, bill_length_mm, bill_depth_mm, flipper_length_mm, body_mass_g, sex, year.
There are three species: Adelie, Chinstrap and Gentoo. There are three islands: Biscoe, Dream, Torgersen. The sex variable contain male and female. The years are 2007, 2008 and 2009. All other variable are number of specific part. 
There are 344 rows and 8 columns.
The mean of  flipper length is 200.915204678363.


